Empirical Study of Scientific Computer Software: Objectives and Research Questions

### 2020-06-03 OverallResearchProposal/ObjectivesAndResearchQuestions.tex
Simplifyin the overall objective to simply be "What is needed to produce sustainable softifacts?"

Define software.

@@

Define softifacts.  In the above definition, software is considered to be an application (app)
and/or a library.  The outcome of the development process is not just software.
It is \{software + artifacts\}.  From this point onward, we will use the term
softifacts when we are referencing the combination of software and the
associated artifacts.  The artifacts consist of such work products as
documentation, build scripts, code, test cases, contributor's guides, etc.  The
quality of sustainability cannot be assessed by looking at the software alone,
or the code alone; it depends on everything, including the processes and
methodologies used during the development.  Further information on the relevant
definitions and context is given in the next section.

@@

>>>>

To understand this research objective, we will decompose each constituent part
in turn, starting with the end of the sentence.  In the above objective,
software consists of either programs, which run (execute) on a computer, or
libraries, which provide services to be used by programs.  Both programs and
libraries are created using computer code, written in a programming language.
Many developers place most, if not all, of their emphasis on the computer code
that makes up programs and libraries.  However, we consider the outcome of the
development process to be more than just software and the associated computer
code; we consider the products of the development process to be \{software +
artifacts\}.  The artifacts include code, but also all the other potential work
products, such as documentation, build scripts, test cases, contributor's
guides, etc.  From this point onward, we will use the term \emph{softifacts}
when we are referencing the combination of software and the associated
artifacts.  As we will see, assessing the quality of sustainability is not
possible by only considering the computer code; it depends on all of the
artifacts, and on the processes and methodologies used during software
development.  \wss{Can we consider software as both the computer code and the
  executable (program or library), or should the term software just mean the
  executable?  That is, when we mean code, should we be careful to not instead
  say software?}

@@

@@

Further information on the relevant definitions and context is given in the next
section.  Roadmap.
